An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates

### 2022-05-30 poly-embed-journal/poly-embed-journal.tex
Section 6-6.2 pass

For example, one of the surrogates is $\Li {4}(u)_y = \left(1 - u_y + \frac 1 k \sum_{i=1}^k (u_{\setminus y})_{[i]}\right)_+$, where $u_{[i]}$ denotes the $i$th largest element of $u \in \reals^n$.
The authors show that $\Li{4}$ embeds $\ell^{(4)}(T)_y = \tfrac {k+1} {k+1-|T|} \ones\{y\notin T\}$, where $T$ is a set of at most $k$ labels.
These embedded losses may therefore be useful in top-$k$ settings where choosing smaller sets may have some benefit, such as a search engine that can use unused space for advertisements.
Using the losses each proposed surrogate embeds, the authors go on to derive constraints on the label distributions under which the proposed surrogates are actually consistent for top-$k$ classification which subsume previous constraints~\citep{yang2018consistency}.
\raft{I did not understand what ``which subsume previous constraints'' meant.  Do we mean the constraints are tighter than the previous constraints of YK?}

@@

We have shown in \S~\ref{sec:poly-loss-embed} a tight connection between embeddings and polyhedral losses.
Here we go beyond polyhedral losses, showing a more general necessary condition for an embedding: a surrogate embeds a discrete loss if and only if it has a polyhedral Bayes risk, or equivalently, a finite representative set (Lemma~\ref{lem:X}).
This result implies that the embedding condition simplifies to matching Bayes risks (Proposition~\ref{prop:embed-bayes-risks}).
It also reveals some deeper structure of embeddings, even down to the geometry of the underlying properties, and the equivalence of various notions of non-redundant predictions.
In particular, we study a natural notion of a ``trimmed'' loss function (Definition~\ref{def:trim-loss}), and connect this definition to both tight embeddings and non-redundancy from property elicitation (Proposition~\ref{prop:embed-iff-trims-equal}).

@@

%% intro to Lemma X
We now present our main structural result in Lemma~\ref{lem:X}, proved in \S~\ref{app:polyhedra}, which will lay the foundation for the rest of this section.
Lemma~\ref{lem:X} observes that (minimizable) losses $L$ with polyhedral Bayes risk have finite representative sets, and derives equivalent conditions on the level sets of the $\prop{L}$ and discrete losses tightly embedded by $L$.
\raft{TODO: Brief description of the result}\jessiet{Attempted. burn if okay}

@@

Previous work from~\citet[Proposition 4]{duchi2018multiclass} realized the significance of matching Bayes risks for calibration with respect to the 0-1 loss.
Proposition~\ref{prop:embed-bayes-risks} broadens this general insight to any discrete loss.
Moreover, their result relies the Bayes risk of the surrogate being strictly concave, whereas polyhedral Bayes risks are never strictly concave.

>>>>

For example, one of the surrogates is $\Li {4}(u)_y = \left(1 - u_y + \frac 1 k \sum_{i=1}^k (u_{\setminus y})_{[i]}\right)_+$, where $u_{[i]}$ denotes the $i$th largest element of $u \in \reals^n$.
The authors show that $\Li{4}$ embeds $\ell^{(4)}(T)_y = \tfrac {k+1} {k+1-|T|} \ones\{y\notin T\}$, where $T$ is a set of at most $k$ labels.
These embedded losses may therefore be useful in top-$k$ settings where choosing smaller sets may have some benefit, such as a search engine that can use unused space for advertisements.
Using the losses each proposed surrogate embeds, the authors go on to derive constraints on the label distributions under which the proposed surrogates are actually consistent for top-$k$ classification which are tighter than previous constraints~\citep{yang2018consistency}.
\raft{I did not understand what ``which subsume previous constraints'' meant.  Do we mean the constraints are tighter than the previous constraints of YK? \jessie{Exactly; burn}}

@@

We have shown in \S~\ref{sec:poly-loss-embed} a tight connection between embeddings and polyhedral losses.
Here we go beyond polyhedral losses, showing a more general necessary condition for an embedding: a surrogate embeds a discrete loss if and only if it has a polyhedral Bayes risk, or equivalently, a finite representative set (Lemma~\ref{lem:X}).
This result implies that the embedding condition simplifies to matching Bayes risks (Proposition~\ref{prop:embed-bayes-risks}).
We also use these result to understand deeper structure of embeddings, even down to the geometry of the underlying properties. %, and the equivalence of various notions of non-redundant predictions.
In particular, we study a natural notion of a ``trimmed'' loss function (Definition~\ref{def:trim-loss}), and connect this definition to both tight embeddings and non-redundancy from property elicitation (Proposition~\ref{prop:embed-iff-trims-equal}).

@@

%% intro to Lemma X
We now present our main structural result in Lemma~\ref{lem:X}, which we prove in \S~\ref{app:polyhedra}.
%This result lays the foundation for the rest of this section.
Lemma~\ref{lem:X} observes that (minimizable) losses $L$ with polyhedral Bayes risk have finite representative sets, and derives equivalent conditions on the level sets of the $\prop{L}$ and discrete losses tightly embedded by $L$.
\raft{TODO: Brief description of the result}\jessiet{Attempted. burn if okay}

@@

%Previous work from~\citet[Proposition 4]{duchi2018multiclass} realized the significance of matching Bayes risks for calibration with respect to the 0-1 loss.
%Proposition~\ref{prop:embed-bayes-risks} broadens this general insight to any discrete loss.
%Moreover, their result relies the Bayes risk of the surrogate being strictly concave, whereas polyhedral Bayes risks are never strictly concave.
